---
title: "Report analysis"
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
params:
  draw_plot: NULL
  width: NULL
  height: NULL
  text: NULL
---

<style type="text/css">

*{
font-size: 16px;
font-family: 'arial narrow';
text-align: justify;
}
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}
h1 {color: darkblue;
    text-align: center;
    font-family: Impact;
    font-size: 35px;
}

code.r, pre {font-size: 14px;
    margin-left: auto;
    margin-right: auto;
    width: 100%;
    background-color: lightyellow;
    border: white;    

</style>

<style>
#TOC {
  background: url("https://redacaonline.com.br/blog/wp-content/uploads/2018/02/logo_uel.jpg");
  background-size: contain;
  padding-top: 100px !important;
  background-repeat: no-repeat;
}
</style>

`r params[["text"]]`

```{r setup, include=FALSE}
if (!is.null(params$draw_plot)){
  knitr::opts_chunk$set(echo = TRUE,fig.width = params$width()/100,fig.height = params$height()/100)}
```

```{r,echo=FALSE}
if (!is.null(params$draw_plot))
  params$draw_plot()
```